---
title: "Database Management"
author: "Nithish Vengadesan"
output: html_document
date: "2023-03-02"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(readr)
library(tidyverse)
library(RSQLite)
library(dplyr)
```



```{r}
olist_files_d <- list.files("Dataset/")
olist_files_d

```

```{r}
prefix <- "olist_"
suffix <- "_dataset.csv"

olist_files <- gsub("olist_","",olist_files_d)
olist_files <- gsub("_dataset.csv","",olist_files_d)
olist_files
```


```{r warning=FALSE}
#setup the connection
connection <- RSQLite::dbConnect(RSQLite::SQLite(),"olist.db")

for (variable in olist_files_d) {
  this_filepath <- paste0("Dataset/",variable)
  this_file_contents <- readr::read_csv(this_filepath)

  table_name <- gsub(".csv","",variable)
  #Remove prefix and suffix 
  table_name <- gsub("olist_","",table_name)
  table_name <- gsub("_dataset","",table_name)
  # table_name <- variable
  
  RSQLite::dbWriteTable(connection,table_name,this_file_contents,overwrite=TRUE)
  
}

RSQLite::dbListTables(connection)

RSQLite::dbDisconnect(connection)
```




```{r}
for (variable in olist_files_d) {
  this_filepath <- paste0("Dataset/",variable)
  this_file_contents <- readr::read_csv(this_filepath)

  table_name <- gsub(".csv","",variable)
  saveRDS(this_file_contents,file=paste0("rdadata/",table_name,".rds"))
  
}
```

```{r}
connection<- RSQLite::dbConnect(RSQLite::SQLite(), "olist.db")
test_connection<- RSQLite::dbConnect(RSQLite::SQLite(), "test.db")
```

# Create Tables with DDL

```{sql connection=test_connection}
CREATE TABLE 'customers'(
'customer_id' VARCHAR(50) PRIMARY KEY,
'customer_unique_id' VARCHAR(50) NOT NULL,
'customer_zip_code_prefix' INT NOT NULL,
'customer_city' VARCHAR(50) NOT NULL,
'customer_state' VARCHAR(5) NOT NULL,
FOREIGN KEY (customer_zip_code_prefix)
    REFERENCES geolocation(geolocation_zip_code_prefix)
);
```

```{sql connection=test_connection}
CREATE TABLE 'geolocation'(
'geolocation_zip_code_prefix' INT,
'geolocation_lat' VARCHAR (50) NOT NULL,
'geolocation_lng' VARCHAR (50) NOT NULL,
'geolocation_city' CHAR(50),
'geolocation_state' CHAR(5),
PRIMARY KEY ('geolocation_zip_code_prefix', 'geolocation_lat','geolocation_lng')
);
```

```{sql connection=test_connection}
CREATE TABLE 'orders' (
'order_id' VARCHAR(50) PRIMARY KEY,
'customer_id' VARCHAR(50) NOT NULL,
'order_status' VARCHAR(255) NOT NULL,
'order_purchase_timestamp' TIMESTAMP NOT NULL,
'order_approved_at' TIMESTAMP,
'order_delivered_carrier_date' TIMESTAMP NOT NULL,
'order_delivered_customer_date' TIMESTAMP NOT NULL,
'order_estimated_delivery_date' TIMESTAMP NOT NULL,
FOREIGN KEY ('customer_id')
  REFERENCES customers('customer_id')
);
```

```{sql connection=test_connection}
CREATE TABLE 'products_category_name_translation'(
'product_category_name' VARCHAR(255)PRIMARY KEY,
'product_cateogy_name_english' VARCHAR(255)
);
```

```{sql connection=test_connection}
CREATE TABLE 'products'(
'product_id'VARCHAR(50) PRIMARY KEY,
'product_category_name' VARCHAR(255),
'product_name_length' INT,
'product_description_length'TEXT,
'product_photos_qty' INT NOT NULL,
'product_weight_g' INT NOT NULL,
'product_length_cm' INT NOT NULL,
'product_height_cm' INT NOT NULL,
'product_width_cm' INT NOT NULL,
FOREIGN KEY ('product_category_name')
  REFERENCES products_category_name_translation ('product_category_name')
);
```


```{sql connection=test_connection}
CREATE TABLE 'sellers' (
'seller_id' VARCHAR(50) PRIMARY KEY,
'seller_zip_code_prefix' INT,
'seller_city' VARCHAR(50) NOT NULL,
'seller_state' VARCHAR(2) NOT NULL,
FOREIGN KEY (seller_zip_code_prefix)
    REFERENCES geolocation(geolocation_zip_code_prefix)
);
```

```{sql connection=test_connection}
CREATE TABLE 'order_reviews' (
'review_id' VARCHAR(50),
'order_id' VARCHAR(50) NOT NULL,
'review_score'INT NOT NULL,
'review__comment_title' VARCHAR(8000),
'review_comment_message' VARCHAR (8000),
'review_creation_date' TIMESTAMP NOT NULL,
'review_answer_timestamp' TIMESTAMP NOT NULL,
FOREIGN KEY('order_id')
  REFERENCES orders('order_id')
PRIMARY KEY ('review_id', 'order_id')
);
```

```{sql connection=test_connection}
CREATE TABLE 'order_items'(
'order_id' VARCHAR(50),
'order_items_id' INT NOT NULL,
'product_id'  VARCHAR(50) NOT NULL,  
'seller_id' VARCHAR(50) NOT NULL,  
'shipping_limit_date' DATE NOT NULL,
'price' DOUBLE NOT NULL,
'freight_value' DOUBLE NOT NULL,
FOREIGN KEY ('product_id') 
  REFERENCES products('product_id'),
FOREIGN KEY ('order_id')
  REFERENCES orders('order_id')
PRIMARY KEY ('order_id', 'order_items_id')
);
```

```{sql connection=test_connection}
CREATE TABLE 'order_payments'(
'order_id' VARCHAR(50) NOT NULL,
'payment_sequential'INT NOT NULL,
'payment_type' VARCHAR(50)NOT NULL,
'payment_installment' INT NOT NULL,
'payment_value' DOUBLE NOT NULL,
FOREIGN KEY ('order_id')
  REFERENCES orders('order_id')
PRIMARY KEY('order_id', 'payment_sequential')
);

```

```{sql connection=test_connection}
CREATE TABLE 'closed_deals' (
'mql_id' VARCHAR(50) NOT NULL,
'seller_id' VARCHAR(50) NOT NULL,
'sdr_id' VARCHAR(50) NOT NULL,
'sr_id' VARCHAR(50) NOT NULL,
'won_date' TIMESTAMP NOT NULL,
'business_segment' VARCHAR(50) NOT NULL,
'lead_type' VARCHAR(50) NOT NULL,
'lead_behaviour_profile' VARCHAR(50) NOT NULL,
'has_company' VARCHAR(50) NOT NULL,
'has_gtin' VARCHAR(50) NOT NULL,
'average_stock' VARCHAR(50),
'business_type' VARCHAR(50) NOT NULL,
'declared_product_catalog_size' INT,
'declared_monthly_revenue' INT,
FOREIGN KEY ('seller_id')
  REFERENCES sellers('seller_id')
FOREIGN KEY('mql_id')
  REFERENCES marketing_qualified_leads('mql_id')
PRIMARY KEY ('mql_id','seller_id')
);
```

```{sql connection=test_connection}
CREATE TABLE 'marketing_qualified_leads'(
'mql_id' VARCHAR(50) NOT NULL,
'first_contact_date' TIMESTAMP NOT NULL,
'landing_page_id' VARCHAR(50),
'orgin' VARCHAR(50) NOT NULL,
PRIMARY KEY('mql_id')
);
```

```{r}
RSQLite::dbDisconnect(test_connection)
```


#Normalisation

Multivalues in 'lead_behaviour_profile'.

#```{sql connection=test_connection}
---behaviour_profile table
CREATE TABLE 'behaviour_profile' (
'behaviour_profile_id' INT PRIMARY KEY,
'lead_behaviour_profile' VARCHAR(50)
);

---lead_behaviour table: Junction table to connect leads to its respective behaviour type(s)
CREATE TABLE 'lead_behaviour'(
'mql_id' VARCHAR(50) NOT NULL,
'behaviour_profile_id' INT
FOREIGN KEY ('mql_id')
  REFERENCES marketing_qualified_leads('mql_id')
FOREIGN KEY ('behaviour_profile_id')
  REFERENCES behaviour_type ('behaviour_profile_id')
);

--- new closed_deals table: closed_deals_1
CREATE TABLE 'closed_deals_1'(
'mql_id' VARCHAR(50) NOT NULL,
'seller_id' VARCHAR(50) NOT NULL,
'sdr_id' VARCHAR(50) NOT NULL,
'sr_id' VARCHAR(50) NOT NULL,
'won_date' TIMESTAMP NOT NULL,
'business_segment' VARCHAR(50) NOT NULL,
'lead_type' VARCHAR(50) NOT NULL,
'has_company' VARCHAR(50) NOT NULL,
'has_gtin' VARCHAR(50) NOT NULL,
'average_stock' VARCHAR(50),
'business_type' VARCHAR(50) NOT NULL,
'declared_product_catalog_size' INT,
'declared_monthly_revenue' INT,
FOREIGN KEY ('seller_id')
  REFERENCES sellers('seller_id')
FOREIGN KEY('mql_id')
  REFERENCES marketing_qualified_leads('mql_id')
PRIMARY KEY ('mql_id','seller_id')
);
#```

# A6 SQL Queries
##read csv
```{r}
closed_deals<-read.csv("G:\\My Drive\\Masters Academic\\Term 2\\Data Management\\Assignment\\Dataset\\olist_closed_deals_dataset.csv")
customers<- read.csv("G:\\My Drive\\Masters Academic\\Term 2\\Data Management\\Assignment\\Dataset\\olist_customers_dataset.csv")
geolocation<-read.csv("G:\\My Drive\\Masters Academic\\Term 2\\Data Management\\Assignment\\Dataset\\olist_geolocation_dataset.csv")
marketing_qualified_leads<-read.csv("G:\\My Drive\\Masters Academic\\Term 2\\Data Management\\Assignment\\Dataset\\olist_marketing_qualified_leads_dataset.csv")
order_items<- read.csv("G:\\My Drive\\Masters Academic\\Term 2\\Data Management\\Assignment\\Dataset\\olist_order_items_dataset.csv")
order_payments <- read.csv("G:\\My Drive\\Masters Academic\\Term 2\\Data Management\\Assignment\\Dataset\\olist_order_payments_dataset.csv")
order_reviews<-read.csv("G:\\My Drive\\Masters Academic\\Term 2\\Data Management\\Assignment\\Dataset\\olist_order_reviews_dataset.csv")
orders<- read.csv("G:\\My Drive\\Masters Academic\\Term 2\\Data Management\\Assignment\\Dataset\\olist_orders_dataset.csv")
products<-read.csv("G:\\My Drive\\Masters Academic\\Term 2\\Data Management\\Assignment\\Dataset\\olist_products_dataset.csv")
sellers<-read.csv("G:\\My Drive\\Masters Academic\\Term 2\\Data Management\\Assignment\\Dataset\\olist_sellers_dataset.csv")
product_category_name_translation<-read.csv("G:\\My Drive\\Masters Academic\\Term 2\\Data Management\\Assignment\\Dataset\\product_category_name_translation.csv")
```

Query 1: What are the top 5 product categories with the highest average review score in 2017?
Query 2: What is the total number of orders and total revenue for each product categoryin 2018 and filter out the top 3?
Query 3: How many buyers purchased multiple products from the same seller?
Query 4: What is the average order value in each Brazilian state?
Query 5:  How many orders for each payment method were cancelled?

```{sql connection=test_connection}
---Q1
SELECT c.product_category_name, AVG(r.review_score) AS avg_review_score 
FROM order_reviews r 
JOIN orders o 
ON r.order_id = o.order_id 
JOIN order_items i 
ON r.order_id = i.order_id 
JOIN products p 
ON i.product_id = p.product_id 
JOIN product_category_name_translation c 
ON p.product_category_name = c.product_category_name
WHERE EXTRACT(YEAR FROM o.order_purchase_timestamp) = 2017 
GROUP BY c.product_category_name_english 
ORDER BY avg_review_score 
DESC LIMIT 5

---Q2
SELECT c.product_category_name, COUNT(DISTINCT o.order_id) AS num_orders, SUM(p.payment_value) AS total_revenue 
FROM orders o JOIN order_payments p 
ON o.order_id = p.order_id 
JOIN order_items i 
ON o.order_id = i.order_id 
JOIN products pr 
ON i.product_id = pr.product_id 
JOIN product_category_name_translation c 
ON pr.product_category_name = c.product_category_name
WHERE EXTRACT(YEAR FROM o.order_purchase_timestamp) = 2018 
GROUP BY c.product_category_name_english
ORDER BY total_revenue
DESC LIMIT 3

---Q3
SELECT COUNT(DISTINCT CONCAT(o.customer_id, ' ', ol.seller_id)) AS num_customers 
FROM orders AS o 
INNER JOIN order_items AS ol 
ON o.order_id = ol.order_id 
GROUP BY ol.seller_id 
HAVING COUNT(DISTINCT CONCAT(o.customer_id, ' ', ol.seller_id)) > 0


---Q4
SELECT o.customer_state, AVG(op.payment_value) AS avg_order_value 
FROM orders AS o 
INNER JOIN order_payments AS op 
ON o.order_id = op.order_id 
INNER JOIN customers AS c
ON c.customer_id= o.order_id
GROUPBY o.customer_state;

---Q5
SELECT o.payment_type, COUNT(o.order_id) AS num_cancelled_orders 
FROM orders AS o 
INNER JOIN order_payments as op
ON op.order_id= o.order_id
WHERE o.order_status = 'canceled' 
GROUP BY o.payment_type;

```

```{r}
#Q1
 top_categories_avg_review_score <- order_reviews %>% inner_join(orders, by = "order_id") %>% inner_join(order_items, by = "order_id") %>% inner_join(products, by = "product_id") %>% inner_join(product_category_name_translation, by = c("product_category_name"="product_category_name_english")) %>% mutate(year = lubridate::year(order_purchase_timestamp)) %>% filter(year == 2017) %>% group_by(product_category_name) %>% summarize(avg_review_score = mean(review_score)) %>% arrange(desc(avg_review_score)) %>% head(5)
top_categories_avg_review_score

#Q2
top_categories_by_revenue <- orders %>% mutate(year = lubridate::year(order_purchase_timestamp))%>%filter(year == 2018) %>% inner_join(order_payments, by = "order_id") %>% inner_join(order_items, by = "order_id") %>% inner_join(products, by = "product_id") %>% inner_join(product_category_name_translation, by = c("product_category_name"="product_category_name_english")) %>% group_by(product_category_name) %>% summarize(num_orders = n_distinct(order_id), total_revenue = sum(payment_value)) %>% head(3)
top_categories_by_revenue

#Q3
num_customers <- orders %>% inner_join(order_items, by = "order_id") %>% group_by(seller_id) %>% summarise(num_customers = n_distinct(paste(customer_id, seller_id))) %>% filter(num_customers > 0) 
num_customers

#Q4
avg_order_value <- orders %>% inner_join(order_payments, by = "order_id") %>% inner_join(customers, by="customer_id")%>% group_by(customer_state) %>% summarise(avg_order_value = mean(payment_value)) 
avg_order_value

#Q5
num_cancelled_orders <- orders %>% filter(order_status == "canceled") %>% inner_join(order_payments, by="order_id") %>% group_by(payment_type) %>% summarise(num_cancelled_orders = n())
num_cancelled_orders
```

# A7

```{r}


